---
title: "Feature Selection"
author: "Ryan Zomorrodi"
date: today
format: dashboard
---

# Results

```{r, include = FALSE}
library(tidyverse)
library(gt)
load("imp.RData")
```

## Row {height=40%}

```{r}
imp %>%
    gt() %>%
    opt_interactive()
```

## Row {height=60%}

### Column

```{r}
#| title: Random Forest
#| fig-height: 8

ggplot(slice_max(imp, `Random Forest`, n = 50)) +
    geom_col(aes(x = `Random Forest`, y = fct_reorder(feature, `Random Forest`))) +
    labs(
        title = "Random Forest Important Factors",
        x = "Mean Decrease Impurity (Scaled)",
        y = "Feature"
    )
```

### Column

```{r}
#| title: Light GBM
#| fig-height: 8

ggplot(slice_max(imp, `Light GBM`, n = 50)) +
    geom_col(aes(x = `Light GBM`, y = fct_reorder(feature, `Light GBM`))) +
    labs(
        title = "Light GBM Important Factors",
        x = "Gain (Scaled)",
        y = "Feature"
    )
```

### Column

```{r}
#| title: Elastic Net
#| fig-height: 8

ggplot(filter(imp, `Elastic Net` != 0)) +
    geom_col(aes(x = `Elastic Net`, y = fct_reorder(feature, `Elastic Net`))) +
    labs(
        title = "Elastic Net Important Factors",
        x = "Coefficient",
        y = "Feature"
    )
```

# Methods

1. Features with near zero variance were filtered out
2. Imputation was performed with bagging
3. Oversampling of the under-represented class was performed using SMOTE
4. Random Forest, Light GBM, and Elastic Net were tuned and fit
    - Random Forest
        - ROC AUC: 0.846
        - Accuracy: 0.933
    - Light GBM
        - ROC AUC: 0.852
        - Accuracy: 0.925
    - Elastic Net
        - ROC AUC: 0.845
        - Accuracy: 0.819

